---
title: "Figure 3 v3"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("Functions.R")
source("Data.R")
```

# Set parameters for kmeans
Set the the value of k for each LC (currently 2 for LC12 and 17, 3 for all others) and the threshold for the minimum number of synapses that a postsynaptic partner has to have with each LC to be included in the kmeans analysis. 
```{r}
all_lcs = c("LC17", "LC12", "LC4", "LC6", "LPLC1", "LPLC2", 
             "LC9", "LC10", "LC11", "LC13", "LC15", "LC16", 
             "LC18", "LC20", "LC21", "LC22", "LC24", "LC25", 
             "LC26",  "LPLC4", "LC28b")

LC_k = c(c(2, 2), rep(3, length(all_lcs)-2))
names(LC_k) = all_lcs
LC_syn_count = rep(10, length(all_lcs))
names(LC_syn_count) = all_lcs
```

# Run PCA and kmeans analysis on each LC population
This code chunk only needs to be run once, since the kmeans clustering results will be saved to a file. 
```{r}
compnum = 10
LC_syn = list() #save the synapse locations, labeled by k means cluster, for 3d plotting
for(lc in all_lcs){
  pca_list = lc_getpca(mat_list[[lc]], DN=NULL, syn_count = LC_syn_count[[lc]], rm_self = TRUE, str=lc)
  lc_kclust = lc_pca_clust(pca_list$PCA, num_comp = compnum, num_clust = LC_k[[lc]], lc)
  k = lc_kclust$kmeans
  lc_syn = neuprint_get_synapses(names(k$cluster), roi="OL(R)") %>% as.data.frame() %>% mutate(bodyid = as.character(bodyid))
  saveRDS(lc_syn, sprintf("output/LC_kmeans/%s_synapses_OL.rds", lc))
  
  LC_syn[[lc]] = left_join(lc_syn, data.frame(bodyid = names(k$cluster), cluster = as.character(k$cluster)), by='bodyid') %>% filter(prepost==1)
  #plotting ready dataframe
  saveRDS(LC_syn[[lc]], sprintf("output/LC_kmeans/%s_syn_clust_k%i_plotting.rds", lc, LC_k[[lc]]))
  # save neuron cluster assignments
  saveRDS(data.frame(bodyid = names(k$cluster), cluster = as.character(k$cluster)), sprintf("outpu/LC_kmeans/%s_cluster_assignments_k%i.rds", lc, LC_k[[lc]])) 
}
saveRDS(LC_syn, "output/LC_kmeans/allLC_synapses.rds")
```

After running the above code once, you can just read it in and adjust the plots.
```{r}
LC_syn = readRDS("output/LC_kmeans/allLC_synapses.rds")
```

# Plotting using plotly 3d interactive plot
It should generate an interactive plot embedded in the R notebook that you can rotate and then click the camera icon to download a snapshot. Just change line 1 to switch between each LC population.
```{r}
lc = "LC6"
LC_df = mutate(LC_syn[[lc]], z = z*(-1), x = x*(-1))

plot_ly(LC_df, x=~x, y=~y, z=~z, 
        type="scatter3d", mode="markers", 
        color=~cluster, 
        colors=c('#1f77b4',"#2ca02c", '#ff7f0e'), size=0.1) %>% 
  layout(scene = list(
    yaxis = list(showticklabels = FALSE, showgrid=F),
    xaxis = list(showticklabels = FALSE, showgrid=F),
    zaxis = list(showticklabels = FALSE, showgrid=F)))

bar = data.frame(x=0,  y=24000, z=-35000:(-35000+2500))
plot_ly(bar, x=~x, y=~y, z=~z,
        type="scatter3d", mode="lines", size=.1)

```

