---
title: "Figure 3 v3"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("R/VPN_cluster_analysis/Functions.R")
source("R/VPN_cluster_analysis/Data.R")
```

# Set parameters for kmeans
Set the the value of k for each LC (currently 2 for LC12 and 17, 3 for all 
others) and the threshold for the minimum number of synapses that a postsynaptic 
partner has to have with each LC to be included in the kmeans analysis. 
```{r}
all_lcs <- c(
  "LC17", "LC12", "LC4", "LC6", "LPLC1", "LPLC2",
  "LC9", "LC10", "LC11", "LC13", "LC15", "LC16",
  "LC18", "LC20", "LC21", "LC22", "LC24", "LC25",
  "LC26", "LPLC4"
)

# Define the number of clusters to use with kmeans.
# Originally: 2 for LC17 and LC12, 3 for all others
# LC_k = rep(3, length(all_lcs))  # To use clusters = 3 for all VPNs
# LC_k = c(c(2, 2), rep(3, length(all_lcs)-2))
LC_k <- c(
  2, 2, 3, 4, 3, 5,
  3, 3, 2, 3, 4, 3,
  3, 3, 3, 3, 4, 3,
  3, 3
)
names(LC_k) <- all_lcs

# Define min number of total synapses for a neuron to be considered
LC_syn_count <- rep(50, length(all_lcs)) # Original was 10
names(LC_syn_count) <- all_lcs
```

# Run PCA and kmeans analysis on each LC population
This code chunk only needs to be run once, since the kmeans clustering results 
will be saved to a file. 
```{r}
# Define the number of PC to use in the PCA (originally: 10)
compnum <- 5

# Save the body ID labeled by k means cluster
LC_kls <- list()

# Save the synapse locations, labeled by k means cluster
LC_syn <- list()

# 3d plotting
LC_plt <- list() # Store the PCA scree and the kmeans elbow plots

for (lc in all_lcs) {
  cat("Processing ", lc, ":\n")

  # Evaluate PCA
  cat("- Evaluting PCA...\n")
  pca_list <- lc_getpca(mat_list[[lc]],
    DN = NULL,
    syn_count = LC_syn_count[[lc]],
    rm_self = TRUE,
    str = lc
  )

  # kmeans cluster using the 'compnum' top components
  cat("- Evaluting kmeans...\n")
  lc_kclust <- lc_pca_clust(pca_list$PCA,
    num_comp = compnum,
    num_clust = LC_k[[lc]],
    lc
  )
  k <- lc_kclust$kmeans

  # Store plots
  LC_plt[[lc]] <- list(
    "scree" = pca_list$eigen_plot,
    "knee" = lc_kclust$withinss,
    "clusters" = lc_kclust$clusters
  )

  # Grab the synapses from neuprint using all the bodyids from the clusters
  cat("- Downloading data from neuprint...\n")
  lc_syn <- neuprint_get_synapses(names(k$cluster), roi = "OL(R)") %>%
    as.data.frame() %>%
    mutate(bodyid = as.character(bodyid))

  # Save dataframe
  saveRDS(lc_syn, sprintf("output/LC_kmeans/%s_synapses_OL.rds", lc))

  # Join the cluster number to the synapses table and save
  LC_syn[[lc]] <- left_join(lc_syn,
    data.frame(bodyid = names(k$cluster), cluster = as.character(k$cluster)),
    by = "bodyid"
  ) %>%
    filter(prepost == 1)

  # Save dataframe
  saveRDS(
    LC_syn[[lc]],
    sprintf(
      "output/LC_kmeans/%s_syn_clust_k%i_plotting.rds",
      lc,
      LC_k[[lc]]
    )
  )

  # Create and store dataframe with body ID and cluster #
  LC_kls[[lc]] <- data.frame(
    bodyid = names(k$cluster),
    cluster = as.character(k$cluster)
  )

  # Save neuron cluster assignments (just body ID and cluster #)
  saveRDS(
    LC_kls[[lc]],
    sprintf(
      "output/LC_kmeans/%s_cluster_assignments_k%i.rds",
      lc,
      LC_k[[lc]]
    )
  )
}

# Save all body ID for all VPN clustering info in a single file
saveRDS(LC_kls, "output/LC_kmeans/allLC_bodyID.rds")

# Save all synapses for all VPN with clustering info in a single file
saveRDS(LC_syn, "output/LC_kmeans/allLC_synapses.rds")

# Save all plots in a file
saveRDS(LC_plt, "output/LC_kmeans/allLC_plots.rds")
```

After running the above code once, you can just read it in and adjust the plots.
```{r}
LC_syn <- readRDS("output/LC_kmeans/allLC_synapses.rds")
```

# Plotting using plotly 3d interactive plot
It should generate an interactive plot embedded in the R notebook that you can 
rotate and then click the camera icon to download a snapshot. Just change line 1
to switch between each LC population.
```{r}
lc <- "LC12"
LC_df <- mutate(LC_syn[[lc]], z = z * (-1), x = x * (-1))

plot_ly(LC_df,
  x = ~x, y = ~y, z = ~z,
  type = "scatter3d", mode = "markers",
  color = ~cluster,
  colors = c("#1f77b4", "#2ca02c", "#ff7f0e"), size = 0.1
) %>%
  layout(scene = list(
    yaxis = list(showticklabels = FALSE, showgrid = F),
    xaxis = list(showticklabels = FALSE, showgrid = F),
    zaxis = list(showticklabels = FALSE, showgrid = F)
  ))

bar <- data.frame(x = 0, y = 24000, z = -35000:(-35000 + 2500))
plot_ly(bar,
  x = ~x, y = ~y, z = ~z,
  type = "scatter3d", mode = "lines", size = .1
)
```

